---
title: "MGD_Analyses"
author: "Erika Carlson"
date: "2024-07-02"
output: html_document
editor_options: 
  chunk_output_type: console
---
------

This document contains research notes and code generated by:

> **Erika R. Carlson**  
> Pharmacology & Toxicology PhD Student  
> University of Texas at Austin  
> erika.carlson@utexas.edu

With assistance from:

> **K. Ryan Thompson**  
> Pharmacology & Toxicology PhD Student  
> University of Texas at Austin  
> kt25399@utexas.edu

------

# Overview

We examined the role of microglia on alcohol-induced neurodegeneration in a rat model of an AUD by depleting microglia with PLX5622 (PLX), a highly selective antagonist of colony-stimulating factor-1 receptor (CSF1R), a receptor kinase critical for survival and proliferation of microglia/macrophages.

Iba1 (ionized calcium binding adapter 1) is a marker of microglia/macrophages.
FJB (FluoroJade-B) is a marker of dying neurons.

Adult male sprague-dawley rats were injected with PLX (50 mg/kg, 10 mL/kg, intraperitoneal (i.p.), every 12 h) for 11 days. During the last 4 days of PLX, rats received ethanol (0-5 g/kg, intragastric (i.g.), every 8 h) in a Majchrowicz paradigm. Tissue was collected during intoxication, 3-6 h post-EtOH (T0).
Blood ethanol concentration (BEC; mg/dL) was determined from tail blood collected 90 min post-dose 7.
Tissue was prepared by phosphate-buffered saline perfusion, brain extraction and bisection, and 24 h post-fix in 4% PFA at 4°C.



# Preliminaries

```{r Load libraries, message = FALSE, warning = FALSE}
library(tidyverse) # for data wrangling
library(rstatix) # for statistical analysis
library(emmeans) # for statistical analysis
library(lme4) # for statistical analysis
library(afex) # dependency for ANOVA analysis
library(ggplot2) # for data visualization
library(ggpubr) # for data visualization
```

```{r Graph theme}
# Custom theme for ggplot2
theme_prism <- function() {
  theme_minimal(base_size = 16) +  # Use a minimal base theme
    theme(
      panel.grid.major = element_blank(),  # No major grid lines
      panel.grid.minor = element_blank(),  # No minor grid lines
      panel.background = element_rect(fill = "white", color = NA),  # White background
      plot.background = element_rect(fill = "white", color = NA),  # White plot background
      axis.text = element_text(color = "black"),  # Black axis text
      axis.title = element_text(color = "black"),  # Black axis titles
      axis.ticks = element_line(color = "black"),  # Black ticks
      axis.line.x = element_line(color = "black"),  # Bottom axis line
      axis.line.y = element_line(color = "black"),  # Left axis line
      legend.position = "right",  # Legend position in x
      legend.justification = "top", # Legend position in y
      legend.background = element_blank(),  # Transparent legend background
      legend.key = element_blank(),  # Remove outline around legend key
      legend.title = element_blank(), # Remove legend key title
      plot.title = element_text(hjust = 0.5, size = 16),  # Centered title
      plot.subtitle = element_text(hjust = 0.5, size = 12)  # Centered subtitle
    )
}
```

```{r}
palette_npg <- c("#E64B35", "#4DBBD5", "#00A087", "#3C5488",
                 "#F39B7F", "#8491B4", "#91D1C2", "#DC0000",
                 "#7E6148", "#B09C85")
```

# Binge statistics

```{r Load and process body weights}
# Indicate path to save results
results_path <- "data/results/"

# Load behavioral intoxication score data
weight <- read_csv("data/weight.csv")

# Check data
slice_sample(weight, n = 6)

# Add unique subject id
weight$id <- paste(weight$Subject, weight$Study, sep = "-")

# Get summary statistics per day overall
weight_common <- weight %>% 
  get_summary_stats(day_01, day_02, day_03, day_04, day_05, day_06, day_07, day_08, day_09, day_10, day_11, type = "common") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/weight_common.csv"))

# Obtain mean ± se starting weight overall
weight_start <- weight_start %>% 
    get_summary_stats(day_01, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/weight_start.csv"))


# Calculate average weight per subject (including FJB outlier)
weight <- weight %>% 
  mutate(mean = rowMeans(select(., day_01, day_02, day_03, day_04, day_05, day_06, day_07, day_08, day_09, day_10, day_11)))

# Get summary statistics
weight_summary <- weight %>%
  get_summary_stats(mean, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/weight_summary.csv"))
weight_summary


# Compute two-sample unpaired t-test on average starting weight
weight_day_01_ttest <- weight %>% 
  filter(id != "19-MGD2") %>% 
  t_test(day_01 ~ Condition) %>% 
  add_significance() %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/weight_day_01_ttest.csv"))
weight_day_01_ttest

# Compute two-sample unpaired t-test on average ending weight
weight_day_11_ttest <- weight %>% 
  filter(id != "19-MGD2") %>% 
  t_test(day_11 ~ Condition) %>% 
  add_significance() %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/weight_day_11_ttest.csv"))
weight_day_11_ttest
```

```{r Load and process intoxication scores}
# Indicate path to save results
results_path <- "data/results/"

# Load behavioral intoxication score data
intox <- read_csv("data/intoxication.csv")

# Check data
slice_sample(intox, n = 6)

# Add unique subject id
intox$id <- paste(intox$Subject, intox$Study, sep = "-")

# Remove FJB outlier
# Calculate average behavioral intoxication score per subject
intox <- intox %>% filter(id != "19-MGD2") %>% 
  mutate(mean = rowMeans(select(., dose_01, dose_02, dose_03, dose_04, dose_05, dose_06, dose_07, dose_08, dose_09, dose_10, dose_11, dose_12)))

# Get summary statistics
intox_summary <- intox %>%
  group_by(Condition) %>%
  get_summary_stats(mean, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/intoxication_summary.csv"))
intox_summary

# Compute two-sample unpaired t-test on average behavioral intoxication
intox_ttest <- intox %>% 
  t_test(mean ~ Condition) %>% 
  add_significance() %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/intoxication_ttest.csv"))
intox_ttest

# Reformat data for two-way ANOVA across doses (time)
intox_long <- intox %>% select(!mean) %>% 
  pivot_longer(cols = dose_01:dose_12, 
               names_to = "time",
               values_to = "score")

# Compute two-way ANOVA for behavioral intoxication across doses
two.way <- intox_long %>% 
  anova_test(dv = score, wid = id, between = Condition, within = time)
two.way

get_anova_table(two.way, correction = "none") %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/intoxication_aov2.csv"))


# Pairwise paired t-test comparisons
# a priori comparisons between drug groups within time
pwc <- intox_long %>% 
  group_by(time) %>% 
  pairwise_t_test(
    score ~ Condition, paired = FALSE, 
    p.adjust.method = "bonferroni"
    )

pwc <- pwc %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/intoxication_pwc.csv"))
pwc

```


```{r Load and process ethanol dose}
# Indicate path to save results
results_path <- "data/results/"

# Load ethanol dose data
dose <- read_csv("data/dose.csv")

# Check data
slice_sample(dose, n = 6)

# Add unique subject id
dose$id <- paste(dose$Subject, dose$Study, sep = "-")

# Remove FJB outlier
# Calculate average dose per day per subject
dose <- dose %>% filter(id != "19-MGD2") %>% 
  mutate(day_01 = rowSums(select(., dose_01, dose_02, dose_03)),
         day_02 = rowSums(select(., dose_04, dose_05, dose_06)),
         day_03 = rowSums(select(., dose_07, dose_08, dose_09)),
         day_04 = rowSums(select(., dose_10, dose_11, dose_12)))

dose <- dose %>% mutate(day_mean = rowMeans(select(., day_01, day_02, day_03, day_04)))

# Get summary statistics
dose_summary <- dose %>%
  group_by(Condition) %>%
  get_summary_stats(day_mean, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/dose_summary.csv"))
dose_summary

# Compute two-sample unpaired t-test on average daily dose
dose_ttest <- dose %>% 
  t_test(day_mean ~ Condition) %>% 
  add_significance() %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/dose_ttest.csv"))
dose_ttest

# Reformat data for two-way ANOVA across days
dose_long <- dose %>% select(id, Condition, day_01, day_02, day_03, day_04) %>% 
  pivot_longer(cols = day_01:day_04, 
               names_to = "time",
               values_to = "dose")

# Compute two-way ANOVA for dose across days
two.way <- dose_long %>% 
  anova_test(dv = dose, wid = id, between = Condition, within = time)
two.way

get_anova_table(two.way, correction = "none") %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/dose_aov2.csv"))
```


```{r Load and process blood ethanol concentrations}
# Indicate path to save results
results_path <- "data/results/"

# Load bec data
bec <- read_csv("data/BEC.csv")

# Check data
slice_sample(bec, n = 6)

# Add unique subject id
bec$id <- paste(bec$Subject, bec$Study, sep = "-")

# Remove FJB outlier
# Calculate average bec per subject
bec <- bec %>% filter(id != "19-MGD2") %>% 
  mutate(mean = rowMeans(select(., run_01, run_02)))

# Get summary statistics
bec_summary <- bec %>%
  group_by(Condition) %>%
  get_summary_stats(mean, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/bec_summary.csv"))
bec_summary

# Compute two-sample unpaired t-test on average behavioral intoxication
bec_ttest <- bec %>% 
  t_test(mean ~ Condition) %>% 
  add_significance() %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/bec_ttest.csv"))
bec_ttest
```


```{r Correlate bec and dose 7}
bec_dose <- full_join(bec %>% select(id, Condition, mean), dose %>% select(id, Condition, dose_01, dose_02, dose_03, dose_04, dose_05, dose_06, dose_07))

bec_dose <- bec_dose %>% mutate(Condition = recode(Condition, "PLX-EtOH" = "PLX", "VEH-EtOH" = "VEH"))

# Calculate correlation between ethanol dose 7 and BEC
cor_bec_dose <- bec_dose %>% group_by(Condition) %>% cor_test(dose_07, mean)

condition_colors <- c("PLX" = "#118040", "VEH" = "#0000FF")


plot1 <- ggplot(data = bec_dose, 
                aes(x = dose_07, 
                    y = mean, 
                    color = Condition)) + 
  scale_fill_manual(values = alpha(condition_colors, 0.5)) +
  scale_color_manual(values = condition_colors) +
  geom_point(aes(shape = Condition, 
                 color = Condition, 
                 fill = Condition), 
             size = 2) + # scatterplot
  scale_shape_manual(values = c(21, 22)) +
  geom_smooth(method = lm, formula = y ~ x, se = FALSE) + # add line of fit
  scale_x_continuous(limits = c(-0.05, 5), expand = c(0, 0.01)) + # set x axis bounds
  scale_y_continuous(limits = c(0, 500), expand = c(0, 0)) + # set y axis bounds
  theme_prism() + # use preset theme for prism-like graph
  ylab("BEC 90 min post-dose (mg/dl)") +
  xlab("Ethanol dose (g/kg)") +
  labs(title = "Correlation between ethanol dose and BEC") + 
  stat_cor(method = "pearson", aes(color = Condition), label.x = 3.17, 
           show.legend = FALSE) # add correlation coefficients to graph
plot1
```

```{r mixed effect model of BEC and dose}
bec_dose_long <- bec_dose %>% pivot_longer(cols = dose_01:dose_07, names_to = "time", values_to = "dose")

bec_dose_long$dose <- factor(bec_dose_long$dose)
bec_dose_long$Condition <- factor(bec_dose_long$Condition)

# Fit the mixed-effects model
model <- lme4::lmer(mean ~ dose * Condition + (1|id), data = bec_dose_long)

# Summary of the model
summary(model)
```


# Iba1 cell counts

The number of Iba1+ cells per 10X image was calculated using the following custom ImageJ macro:

```{macro eval = FALSE}
run("8-bit");
setAutoThreshold("Default dark no-reset");
//run("Threshold...");
setThreshold(80, 255, "raw");
//setThreshold(80, 255);
run("Convert to Mask");
run("Convert to Mask");
run("Analyze Particles...", "size=30-Infinity pixel circularity=0.15-1.00 show=[Bare Outlines] summarize");
```


## Add treatment information to ImageJ cell counts

```{r Load and clean Iba1 cell counts}
# Indicate path to files
path <- "data"

# Create vector string of specific files in folder
csv_path <- list.files(path, full.names = TRUE, 
                        pattern = "*.csv", recursive = FALSE)

# Filter to files of interest
csv_path <- grep("Iba1", csv_path, value = TRUE)

# Create data frame to extract data from specific column
# Tell it where to look
rawdata_csvread <- function(.path = path) {
  
  meta <- read_csv(.path) 
  
  # Separate based on image naming convention (JM vs ERC)
  if(str_detect(meta$Slice[1], " ")) {
  meta <- meta %>% 
  .$Slice %>% str_split(" ") %>% 
  unlist() %>%
    matrix(ncol = 6, byrow = TRUE) %>%
    as_tibble() %>%
    rename("Study" = "V1",
           "Subject" = "V2",
           "Slide" = "V3",
           "Slice" = "V4",
           "Region" = "V5",
           "Magnification" = "V6") %>% 
    add_column(.before = "Study", Stain = "Iba1") %>% 
    mutate(Subject = as.numeric(Subject)) %>% 
    mutate(Subject = sprintf("%02d", Subject))
  
  metadata_df <- meta %>%
    select(Stain, Study, Region, Subject, Slice) %>% 
   
    # Rename for consistency in region name
    mutate(Region = case_when(
      Region == "hippo" ~ "Hippo",
      Region == "rhinal" ~ "Rhinal",
      TRUE   ~ Region))
  } else {
  meta <- meta %>% 
  .$Slice %>% str_split("_") %>% 
  unlist() %>%
    matrix(ncol = 5, byrow = TRUE) %>%
    as_tibble() %>%
    rename("Stain" = "V1",
           "Study" = "V2",
           "brainbit" = "V3",
           "Region" = "V4",
           "Magnification" = "V5")
  
  names <- str_extract(meta$brainbit, pattern = "\\d+-\\d+-\\d+") %>%
    str_split("-")
  
  names_df <- names %>% unlist() %>%
    matrix(ncol = 3, byrow = TRUE) %>%
    as_tibble() %>%
    rename("Subject" = "V1",
           "Slide" = "V2",
           "Slice" = "V3") %>% 
    mutate(Subject = as.numeric(Subject)) %>% 
    mutate(Subject = sprintf("%02d", Subject))
  
  metadata_df <- bind_cols(meta, names_df) %>%
    select(Stain, Study, Region, Subject, Slice) %>% 
    
    # Rename for consistency in region name
    mutate(Region = case_when(
      Region == "Ento" ~ "Rhinal",
      TRUE   ~ Region))
  }

  # Make a data frame for Counts from excel file  
  select_data <- read_csv(.path) %>% 
    select(Count)

  # Combine Count data frame into one with metadata
  select_data_meta <- bind_cols(metadata_df, select_data)
  return(select_data_meta)
}

# Each time it maps it takes a different item of those within csv_df
csv_df <- map(csv_path, rawdata_csvread) %>% bind_rows()

# Add a column to differentiate same number subjects during analysis
csv_df$id <- paste(csv_df$Subject, csv_df$Study, sep = "-")

# Check data
slice_sample(csv_df, n = 6)
```


## Calculate average per subject per region, attach condition

```{r}
# Calculate summary statistics per subject
csv_counts_bysubject <- csv_df %>% 
  select(id, Region, Count) %>% 
  group_by(id, Region) %>% 
  summarize(Iba1_avg = mean(Count),
            Iba1_sd = sd(Count),
            slices = n(),
            Iba1_sem = Iba1_sd/sqrt(slices)) 

# Read in treatment info, split Condition into variable components
condition <- read_csv("data/MGD_subjects.csv") %>% 
  mutate(Subject = sprintf("%02d", Subject)) %>% 
  separate(Condition, c('Drug', 'Diet'), remove = FALSE)

# Add unique subject id to treatment info
condition$id <- paste(condition$Subject, condition$Study, sep = "-")

# Add condition to counts per subject, joining by region and id
# Remove FJB outlier
csv_counts_bysubject_condition <- left_join(csv_counts_bysubject, condition) %>% 
  group_by(id) %>% 
  arrange(Region, Diet, desc(Drug)) %>% 
  filter(id != "19-MGD2")

# Calculate percentage change
csv_counts_sum <- csv_counts_bysubject_condition %>% 
  select(id, Region, Drug, Diet, Iba1_avg) %>% 
  group_by(Region, Diet, Drug) %>% 
  summarize(mean = mean(Iba1_avg)) %>% 
  ungroup() %>%
  pivot_wider(names_from = 'Drug', values_from = 'mean') %>% 
  mutate(percent_loss = (`VEH` - `PLX`) / `VEH` * 100)
csv_counts_sum

# Export .csv files
results_path <- "data/results"

write_csv(csv_counts_bysubject_condition, 
        str_c(results_path, "/Iba1_counts.csv"))

write_csv(csv_counts_sum, 
        str_c(results_path, "/Iba1_percentdiff.csv"))
```


## Statistical analysis of Iba1 cell counts

```{r Iba1 analysis}

iba1 <- read_csv("data/results/Iba1_counts.csv", col_names = TRUE)

results_path <- "data/results"

# Check data
slice_sample(iba1, n = 6)

# Compute two-way ANOVA for hippocampus
two.way <- iba1 %>%
  filter(Region == 'Hippo') %>% 
  anova_test(dv = Iba1_avg, wid = id, between = c(Drug, Diet))
two.way

get_anova_table(two.way) %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/Iba1_counts_hippo_aov2.csv"))


# Pairwise paired t-test comparisons for hippocampus
# a priori comparisons between drug groups within diet
pwc <- iba1 %>%
  filter(Region == 'Hippo') %>% 
  group_by(Diet) %>% 
  pairwise_t_test(
    Iba1_avg ~ Drug, paired = FALSE, 
    p.adjust.method = "bonferroni"
    )

pwc <- pwc %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/Iba1_counts_hippo_pwc.csv"))
pwc
# Significant effect of drug for both CON and EtOH


# Compute two-way ANOVA for rhinal cortex
two.way <- iba1 %>%
  filter(Region == 'Rhinal') %>% 
  anova_test(dv = Iba1_avg, wid = id, between = c(Drug, Diet))
two.way

get_anova_table(two.way) %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/Iba1_counts_rhinal_aov2.csv"))
# Significant main effect of drug


# Pairwise paired t-test comparisons for rhinal cortex
# a priori comparisons between drug groups within diet
pwc <- iba1 %>%
  filter(Region == 'Rhinal') %>% 
  group_by(Diet) %>% 
  pairwise_t_test(
    Iba1_avg ~ Drug, paired = FALSE, 
    p.adjust.method = "bonferroni"
    )

pwc <- pwc %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/Iba1_counts_rhinal_pwc.csv"))
pwc
# Significant effect of drug
```



# FJB cell counts

The number of FJB+ cells per region per tissue slice was counted by hand and averaged across the number of slices containing that region.

```{r}
results_path <- "data/results"

fjb <- read_csv("data/FJB.csv", col_names = TRUE)

# Check data
slice_sample(fjb, n = 6)

# Add unique subject id
fjb$id <- paste(fjb$Subject, fjb$Study, sep = "-")

# Separate Condition into Drug and Diet columns for two-way ANOVA analysis
# Remove outlier (19-MGD2, >300 FJB+ cells in one ventral hippocampal section)
# Rearrange Hippo and Rhinal columns into Region and Counts columns 
fjb <- fjb %>% 
 mutate_at(vars(Condition), factor) %>% 
  separate(Condition, c('Drug', 'Diet'), remove = FALSE) %>% 
  filter(id != "19-MGD2") %>% 
  pivot_longer(cols = c("Hippo", "Rhinal"), 
               names_to = "Region", values_to = "Count")

# Get summary statistics
fjb_grouped <- fjb %>%
  group_by(Region, Condition) %>%
  get_summary_stats(Count, type = "mean_se") %>% 
  as_tibble() %>% 
  write_csv(., str_c(results_path, "/FJB_summary.csv"))
fjb_grouped


# two-way ANOVA for hippocampus
aov2_fjb_hippo <- aov_ez(id = 'id', 
                         dv = 'Count', 
                         data = fjb %>% filter(Region == 'Hippo'), 
                         between = c('Diet', 'Drug')
                   )
aov2_fjb_hippo

# Add significance label and save result as tibble
anova(aov2_fjb_hippo) %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  rename(p = "Pr(>F)") %>% 
  mutate("p<.05" = case_when(p < 0.0001 ~ "****",
                             p < 0.001 ~ "***",
                             p < 0.01 ~ "**",
                             p < 0.05 ~ "*",
                             p >= 0.05 ~ "ns")) %>% 
  write_csv(., str_c(results_path, "/FJB_counts_hippo_aov2.csv"))
# Significant main effect of drug, diet, and interaction


# Post-hoc comparisons restricted to common factors with contrasts[c()]
# Add significance labels
post_aov2_fjb_hippo <- emmeans(aov2_fjb_hippo, 
                                pairwise ~ Diet * Drug,
                                adjust = "bonferroni")$contrasts[c(1,2,5,6)] %>%
  as_tibble() %>%
  mutate("p<.05" = case_when(p.value < 0.0001 ~ "****",
                             p.value < 0.001 ~ "***",
                             p.value < 0.01 ~ "**",
                             p.value < 0.05 ~ "*",
                             p.value >= 0.05 ~ "ns")) %>% 
  write_csv(., str_c(results_path, "/FJB_counts_hippo_aov2_posthoc.csv"))
post_aov2_fjb_hippo
# Significant differences: EtOH PLX - EtOH VEH and CON VEH - EtOH VEH



# two-way ANOVA for rhinal cortex
aov2_fjb_rhinal <- aov_ez(id = 'id', 
                         dv = 'Count', 
                         data = fjb %>% filter(Region == 'Rhinal'), 
                         between = c('Diet', 'Drug')
                   )
aov2_fjb_rhinal

# Add significance label and save result as tibble
anova(aov2_fjb_rhinal) %>%
  rownames_to_column(var = "Factor") %>%
  as_tibble() %>% 
  rename(p = "Pr(>F)") %>% 
  mutate("p<.05" = case_when(p < 0.0001 ~ "****",
                             p < 0.001 ~ "***",
                             p < 0.01 ~ "**",
                             p < 0.05 ~ "*",
                             p >= 0.05 ~ "ns")) %>% 
  write_csv(., str_c(results_path, "/FJB_counts_rhinal_aov2.csv"))
# Significant main effect of drug, diet, and interaction


# Post-hoc comparisons restricted to common factors with contrasts[c()]
post_aov2_fjb_rhinal <- emmeans(aov2_fjb_rhinal, 
                                pairwise ~ Diet * Drug,
                                adjust = "bonferroni")$contrasts[c(1,2,5,6)] %>% 
  as_tibble() %>%
  mutate("p<.05" = case_when(p.value < 0.0001 ~ "****",
                             p.value < 0.001 ~ "***",
                             p.value < 0.01 ~ "**",
                             p.value < 0.05 ~ "*",
                             p.value >= 0.05 ~ "ns")) %>% 
  write_csv(., str_c(results_path, "/FJB_counts_rhinal_aov2_posthoc.csv"))
post_aov2_fjb_rhinal
# Significant differences: EtOH PLX - EtOH VEH and CON VEH - EtOH VEH
```

